A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-04-18 graph_syntax.tex

These operations, though very simple, are effectively the same kind of task 
performed by an analysis block. A constraint or objective function can therfore 
be represented as another analysis block on the graph, with it's own input and 
output variable nodes. Although fundamentally no different than an analysis block, 
for clarity and convience it is useful to distinguish between regular analysis 
blocks and those that arise from the addition of objectives or constraints to 
	the graph. Therefore, we define an \emph{expression block} as the collection of variable and model 
	nodes related to a given objective or constraint function. Fig.~\ref{f:obj-cons}
shows a notional problem graph augmented with expression blocks and appropriate 
connection edges.

>>>>

These operations, though very simple, are effectively the same kind of task 
performed by an analysis block. A constraint or objective function can therfore 
be represented as another analysis block on the graph, with it's own input and 
output variable nodes. Although fundamentally no different than an analysis block, 
for clarity and convience it is useful to distinguish between regular analysis 
blocks and those that arise from the addition of objectives or constraints to 
the graph. Therefore, we define an \emph{expression block}, as the collection of variable and model 
nodes related to a given objective or constraint function. Fig. \ref{f:obj-cons}
highlights the objective and constraint blocks from the Sellar problem.
